A thesis draft

### 2018-11-28 res/sections/08-Background.tex
Other minor fixes
Fix image size
Fix image position

\section{The 5G connectivity standard}

@@

\subsection{5G architecture}

@@

\section{The VIBeS project}
This thesis started as a part of the VIBES project~\cite{vibesesa}, whose main
requirement is to enhance the performance of end-to-end IP based that involves
satellite connections. To reach this goal, the project specifications suggest to
exploit the 5G incoming technology and use the NFV-MANO architecture to perform
first packets elaboration and performance improvement and finally TCP/IP
satellite chunk optimization with the Performance Enhancing Proxy (PEP). The
VIBES project proposed five technical requirements:
\begin{enumerate}
  \item Analysis of the applicability of current and new Internet protocols in
  the proposed VNF-PEP architecture
  \item Implementation of a VNF-PEP prototype
  \item Building of a PoC test platform
  \item VNF-PEP validation and performance tests on 5G use-cases
  \item Demonstration test-bed management
\end{enumerate}

\begin{figure}[t]
 \centering
 \includegraphics[scale=1]{vibes_logo}
 \caption{ViBeS project logo}
 \label{chap:background:img:vibes_logo}
\end{figure}

@@

>>>>

\section{Fifth generation mobile networks}

@@

\subsection{5G 3GPP MANO}

@@

\section{The VIBeS project}

This thesis started as a part of the VIBES project~\cite{vibesesa}, whose main
requirement is to enhance the performance of end-to-end IP based that involves
satellite connections. To reach this goal, the project specifications suggest to
exploit the 5G incoming technology and use the NFV-MANO architecture to perform
first packets elaboration and performance improvement and finally TCP/IP
satellite chunk optimization with the Performance Enhancing Proxy (PEP). The
VIBES project proposed five technical requirements:
\begin{enumerate}
  \item Analysis of the applicability of current and new Internet protocols in
  the proposed VNF-PEP architecture
  \item Implementation of a VNF-PEP prototype
  \item Building of a PoC test platform
  \item VNF-PEP validation and performance tests on 5G use-cases
  \item Demonstration test-bed management
\end{enumerate}

@@

\begin{figure}[h]
 \centering
 \includegraphics[scale=1]{vibes_logo}
 \caption{ViBeS project logo}
 \label{chap:background:img:vibes_logo}
\end{figure}
